Towards Automated Refactoring of Code Clones in Object-Oriented Programming Languages\\- Work in Progress -

### 2019-07-01 sattose/paper.tex
Let's move this up
Made this formula shorter

To limit the negative impact of this tradeoff on the design of the system, we formalized as threshold for the variability between fragments. The formula by which this threshold is calculated is displayed in equation \ref{eq:type2r}. We take the amount of literals, variables and method calls that differ from other clone instances in a clone class and divide it by the total number of tokens in the clone instance. Based on this threshold, we decide whether a clone should be considered for refactoring.

\begin{equation}\label{eq:type2r}
\text{T2R}=\frac{\text{Different expressions}}{\text{Total tokens}}*100
\end{equation}
$$Diff = \text{Number that differ from other clone instances}$$
$$l = \text{Literals in clone instance}$$
$$v = \text{Variables in clone instance}$$
$$m = \text{Method calls in clone instance}$$

>>>>

To limit the negative impact of this tradeoff on the design of the system, we formalized as threshold for the variability between fragments. The formula by which this threshold is calculated is displayed in equation \ref{eq:type2r}. In this formula, \textit{different expressions} refers to the amount of literals, variables and method calls that differ from other clone instances in a clone class. We divide this by the total number of tokens in the clone instance. Based on this threshold, we decide whether a clone should be considered for refactoring.

\begin{equation}\label{eq:type2r}
\text{T2R}=\frac{\text{Different expressions}}{\text{Total tokens}}*100
\end{equation}
